Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
evaluation

Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.

\begin{hyp}
The fact that only 1/5 of all violations result from vocabulary constraints, 
even though, 46\% of all constraints are vocabulary constraints,
indicates good data quality in general (according to formal specifications of vocabularies).
\end{hyp}

>>>>

Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
The fact that only 1/5 of all violations result from vocabulary constraints, 
even though, 46\% of all constraints are vocabulary constraints,
indicates good data quality in general with regard to the formal specifications of vocabularies.
\begin{hyp}
For all vocabularies, data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
\end{hyp}
